\documentclass[../FGP.tex]{subfiles}
\renewcommand\thepage{\arabic{page}}
\begin{document}

\section{Consult}
\begin{fragment}The book -- if the singular \emph{book} was even appropriate -- was unlike any she had seen in years of hard study. One page fell out into yards of inserts and appendices, and then those appendices unfolded into scrolls of errata and emendations running parallel to the book's spine for meters before they came to another insert with its own set of errata and the process continued on and on, in tinier and more cramped hands with each succession. 

Irene looked on in wonderment while a small committee of royal librarians, dressed in an assemblage of green robes that suggested a witch's cloak that had gone up in society and then lost its way, worked to unravel the last of the pages. Once, as part of her apprenticeship, she had been told to speak with an oak. This was, in fact, a misnomer, because oaken communication was largely a series of  mental images that  rolling across her brain, and when the oak had said `I' she had seen something of the same tangle of roots descending from trunks to thin white rhizoids as she did in the scripts' endless branching into subcases and strata more and more obscure.  

After the rustling of pages had finally settled, the leader of the committee cleared her throat and with visible relief the sub-librarians and the poor devils of sub-sub-librarians assisting her filed out of the room. When they were gone the chief librarian produced a quill from her robes and, after fumbling with the tails of the book, eventually settled upon an empty strand of paper. 

Princess Zelda spoke evenly, in a voice Irene could almost mistake for indifference if she didn't recognize it from Gram trying to keep an even temper, ``why do you believe you have irreparably shifted Hyrule off of its natural historical course?''  
\end{fragment}

\begin{fragment}
``I think, as far as attitudes toward the recording of history goes, it would be fair to call us `pro-copious.'{''} the Chief Librarian offered. 
\end{fragment}
\end{document}