\documentclass[../FGP.tex]{subfiles}
\begin{document}
\section{Eclipse}
\begin{fragment}
%% MEANWHILE, BEFORE ELE, has a guy who mentions his horses need to be shod in passing and she recommends Link as a farrier. Then wonders if she shouldn't have since it'll give people Ideas.
\end{fragment}
\begin{fragment}
The sun glinted off the myriad glazes on the ceramics Irene had set out before her, and again she stole an envious look into the Witch's hut where Gram, by dint of seniority, conducted her consultations indoors. Squinting away the glare, she reached for a blue solution -- not yet a full potion, but give it two monster tails and time on the fire and it could be -- and an empty jar, into which she decanted half. 

``Give `im two sips of this an evening for the fever 'til symptoms improve and--'' she was blanking again, how did Gram keep them all straight ``what'd you say the other thing was?''

``My daughter needs--''

``-- a potion of invulnerabilty! --''\qquad
``-- an antiseptic. What? \emph{Ele}!''\footnote{Reminder: Ele is short for Eleuthera.}

It took Irene a moment to parse out the two different voices, and a moment more to understand `invulnerability' though the child's mispronunciation, before turning towards Ele. 

``What do you need invulnerability for?''

``I'm going to ride a lynel,'' she answered with an indifferent confidence that suggested the lynel-riding was merely instrumental in some grander scheme she did not deign to share.

``Not if you have a festering wound you aren't. Where are you injured?''

The girl rolled her sleeve up to reveal an elbow covered in abraisions, with splinters at her wrist. ``A lynel shot me and I died,'' she explained. Irene was very proud of not laughing aloud and over Ele's head her mother mouthed `she fell.' Irene wondered whether she ought stop to get the true story out of the girl, to build good patient habits, but another look at the line wending its way around the hut decided against it -- too many other people to make wait. ``But you can treat arrowwounds!'' the girl chirped with an enthusiasm rare in the recently deceased. ``They say the Hero got shot full of them and you pulled them out and healed him.'' 

Irene froze as the image of Link, bloodied and skin-pierced from head to toe, formed unbidden in her mind.  Her blood stopped dead in her veins a moment before she managed ``You must be thinking of someone else because I don't know a thing about that if it happened, and I certainly wasn't the one to tend `im, but I do know you shouldn't yank arrows out of a person.''

It was a brusquer answer than a child deserved, but if she didn't stop the rumor now she feared half her consultations would be nothing but questions about Link's heroics. Still, she made sure to offer an apologetic smile to both girl and mother as she fetched another small jar. She handed the jar to the mother and made sure to address Ele -- in a voice loud enough the mother was sure to hear, too -- while explaining. 

``Ointment. Pummelled verderoot in bosun's oil. Apply it once now, and then when you wake up and go to bed for three days. Might sting a little, but it's an ant bite next to a lynel's bow.'' 

Ele looked at the jar solemly while her mother offered a thanks and a blue rupee. Irene had been hoping for a red, but accepted the payment and wished them both safe travels back to town. 

``Next!'' she shouted, as a man with an arm in a sling ambled up. 

He'd broken his favored arm judging by the side of his belt he kept his satchel on, and the fumbling with the stool as he tried to take a seat, but through it all he offered high spirits and a bucktoothed smile. It was a familiar smile, though Irene couldn't say from where.  
\end{fragment}
\begin{fragment}
 %% Treasure hunter with broken arm. "Hey can you tell Link to leave a note if he's already got the treasure?" She starts reading him the riot act and gets cut off midway through by the Emergency peal of the bell. 
 %% 
 %%

\end{fragment}
\end{document}