%!TEX encoding = UTF-8 Unicode
\documentclass[../FGP.tex]{subfiles}

\renewcommand\thepage{\arabic{page}}
\pagestyle{empty}
\usepackage{lettrine}
\usepackage{fontspec}
%\renewcommand\footnote[1]{}
%\RenewDocumentCommand\marginnote{s+m}{}
%\def\setmarginpargeometry{}%
%  \newgeometry{textwidth=260pt,marginparwidth=150pt}
%  \edef\marginnotetextwidth{\the\textwidth}
\begin{document}
\setmarginpargeometry
\section{Fortune}
\noindent \label{sec:fortune}\lettrine[lines=3,loversize=0.039]{I}{rene looked up}%
\marginnote{Quick note to self: I think you have three problems with this draft. i) I don't think this gives enough room to Irene's growing problem with fate vs her own reputation. ii) I don't think this does a good job of setting context (making clear this is a few years after LBW, making clear how Link picked up astrology in Labrynna etc.) iii) I think this does a really \emph{bad} job of spelling out the inform-but-don't-interfere rule of witchcraft that Irene sets herself up to break in this chapter.}
from her work, bit her lip, and glowered at the myriad suns and distant galaxies scattered across the black. If there were portents in the stars -- and she was most certainly not conceding that there were -- Irene wanted nothing to do with them. The very premise had something insulting in it. Reading palms or tea leaves, their subjects as rough and varied as the lives they predicted, required work and more than a little art. The charting of stars required a few pages of records and maybe an hour of computation. Irene could change lead into gold, or a bead into a bandicoot, but not a life into arithmetic, and whatever sense of professionalism might keep a better witch from crowing at an astrologer's failures, Irene lacked it -- and it was far too late to worry about professionalism, anyway.

``Net pull is weak, two or three--'' the astrologer mumbled. Irene hadn't a clue what two or three was measured in, but he seemed to be talking for his own sake at the moment ``-- and it's\ldots five degrees, no ten toward{\ldots} um{\ldots}''

A turtle glid serenely through the cosmos, before coming to an amenably smooth rock at the end of the visible universe and climbing half-way out. Behind it trailed a rippling wake that washed the million points of light from visibility; Irene beamed.

\normalmarginpar``Interference!'' Link whined, ``this go doesn't count."  

``Does so." 

``Oh come on. I can't finish the stars now until the pond settles, and you're still reading my palm" She wasn't; she was too giddy.

``If you don't like it you're always free to use the actual thing,'' Irene said, motioning upwards to the night sky above them, boxed in by the courtyard's walls and occluded by clouds, none of which appeared in the water below them. ``I'm already giving you a leg up, you know.''

``But--'' 

Irene scooped water from the enchanted pool with her free hand and flicked. 

``Okay! Okay! Fine,'' he said in a voice clearly indicating he was anything but, and indeed might die at any moment, but whatever his pains he recovered quickly ``there really \emph{is} a reading to take from the clouds. They filter the stars' influence, so depending which are covered right now\ldots'' and back he went to mathematical muttering. Which stars were covered seemed like and open and closed case to Irene's eyes, clouds evenly smothered the whole of the sky, and after the incident with the turtle, all that was left to light the yard were a set of torches sconced in the castle walls and the glow of an acorn that Irene had enchanted earlier for a reading aide. The latter of these suffused Link's face, and she could see the focus in his eyes as he peered intently out into space, his lip twitching in consternation at meanings she did not credit were there, not really, but he gawked with such conviction that some part of her wondered if there might be something to the starry mumbo-jumbo he had dragged back from Labrynna after all.%
    %\marginnote{Before pubilishing decide for sure if you want this to be Labrynna or the drablands instead}
That wondering was idle, the other parts snapped. This was a competition and if star-reading had any foundation it could win fair and square against her preferred style of divination,\footnote{viz., literally anything else, except maybe vegemancy.\footnotemark[2]}\footnotetext[2]{Vegemancy foretold events by readings of greenery, but its practitioners were bitterly -- often violently -- divided over whether you were supposed to take the reading off the leaves of arecaceous plants (the so-called ``frondhead'' vegemancers) or off the corms of certain asteraceous plants (``rooter'' vegemancers). The feud was entirely off-putting to other practitioners of magic.}\marginnote{This is a great joke, but doesn't feel natural here and probably needs to go elsewhere.} and to do that she had to start in on actually reading. The only barrier being--
 
 ``Stop squirming.''

 ``I'm not!'' And he sent forth a tiny spray of water in revenge, but stilled all the same. Even with his palm steady, the low light proved a burden, and Irene had to scoot and shift her seat around him until she was nearly over his shoulder so that, when she leaned in, she did not cover the hand in shadow.

Once on her broom she had looked down over Zora's River and realized the hills of eastern Hyrule were ancient riverbanks whose river had wandered off.%
    \normalmarginpar\marginnote{\textit{Cf.} \textit{Ancient courses within the Mississippi River meander belt} (illustration) \textit{in} \textsc{Harold N.\ Fisk, U.S.\ Army Corps of Eng'rs., Geological Investigation of the Alluvial Valley of the Lower Mississippi River} (1944), \textit{available at} \url{https://biotech.law.lsu.edu/climate/mississippi/fisk/plate_22-2.pdf} (real example of same phenomenon). This makes Zora's River an alluvial distributary system, which isn't supported by evidence from \textsc{LBW} or \textsc{LttP}, but I like this metaphor enough I think I'll take artistic license.}
Rolling hills curl\-i\-cued around the ghost of an oxbow, while three miles west the River ran straight. A bluff overlooked a valley that once must have been part of the Eastern Palace's moat, and now the River wended lazily around Hyrule Castle. Where now it bent west, in some age or other past it bowed east, and so on in a thousand variations on the same watery journey, always emptying into Lake Hylia. Link's palm was like that. What she initially thought was a severely bifrucated Life line, crossed and pockmarked by occlusions was, in  fact scores upon scores of Life lines all run together. Once realized, it shocked her how easily she picked out her Link from the tangle, and could trace the line as it turned toward the Mount of Apollo, like all the hundred others. His Heart line ran deep and clear, which was no surprise to her, and like all the others it doubled back up to the Mount of Jupiter before running a short distance and vanishing somehwere on the pads below his ring finger. 

A thousand meandering variations, all ending in the same place. The flow of time was cruel, indeed.

\normalmarginpar``--the brightness of {\Gr µ}-thulan\ldots{} or the Peninsular Star? I didn't know it bothered you.'' There was a note of genuine apology in his voice.

``What?'' It was only after asking that Irene realized she had flinched, and that Link thought it was something he'd said. She was going to have to explain, now, when she had only the vaguest preomonition of what was even wrong -- and even if she did understand, what could say? ``Oh, not that. Don't get me wrong the Labrynnan names are dry as a \emph{bone}, but-- Link, there's something terrible in your future.''  

``Future in the next few days? Weeks?'' he said, handling doom with a calm that, on reflection, should not have surprised her.

``Further out than that.'' She was sure of that much, at least, but what was she allowed to tell? ``\ldots Months?''

Link gave a simple resolute nod, and it perturbed her how much even in this he seemed to be accepting an assignment. 
``Then I have both time and excellent counsel.'' 
It was true, but hearing it somehow made everything worse.\marginnote{She's reacting -- subconsciously -- to what I can only describe as the performative streak in this response. Having a response so polished ready to go disconcerts her because half of her worry is how much time he's doing work on behalf of the Royal family and seeing him develop courtly skills\ldots} 

``However I can, I'll help.''

The conversation hung silent for a moment before Link mumbled an ``anyway'' and turned his head back toward the pool, and hung on for a moment longer while Irene processed his reaction. 

``You're \emph{still} on that?'' she exclaimed once she realized to where his attenion had turned ``''Now, of all times?'' 

``Well I promised a fortune reading for one,'' he said in that same bewilderingly calm tone ``and this late at night it's not like there's an octoball game to join.''

It had to be at least partially an act, she thought, and pushed away a pang of hurt that he felt he had to keep the performance going for her. But then again, how often had she flown in only to find him dodging cuccos when the world was at stake? Maybe it really was normal -- well, normal for him -- stress management.

Maybe, but she'd known the peril to all the world then, too, and this felt different to her.

He'd could simply have been stewing in heroism too long, she supposed. Gram had always warned her about the difference between feeling urgency and panic, and never to lose one when you tamped down the other. But it wasn't like anyone taught Link heroics, people told him about old curses in older temples and then he dove headlong inside them and everyone breathed easier. Save a country or a village or a world often enough and maybe mortal peril just stopped registering. That explanation felt incomplete, though. It wasn't like there was any shortage of times he'd rung her to side-step monster encounters. For that matter, there was no shortage of times he'd rung her after a long battle to get to a fairy fountain, or just to bum red poition. He'd seemed to understand urgency perfectly well then. She searched his face as he worked for a clue to his thoughts, but found only a look of concentration give way to one of confusion.

``What is it?''

``I can't get an answer.'' He said in a tone take took all joy out of victory. ``It's -- once you've got a readings of the stars, you try to project\ldots there's a part where you find the tip of a cone, only with this reading there's no cone at all, and it all just circles and circles without an answer.''

Her mouth opened briefly, then closed again when she realized she had no clue what to say. Telling him none of his starry mechanics was real wasn't any consolation to him, and pretending she believed it meant believing the intolerable, even if Link hand't realized it yet. There was an easy explanation for why Link could not read her future: she didn't have one. Not that she feared death, she'd read her own Head line and knew she had ages. A long life without any further events of note, however, felt discomfitingly plausible. But that was a problem she only had if she believed nonsense, and even assuming it were true she -- by definition -- had a long and healthy life to address it. Link was the one with the crisis.

From the north wall echoed the clank of armor on stone; the guards were changing shifts.

``I know there's a way to get an answer out, but I don't think I'm likely to find it tonight.''

``Rain check?'' She asked as she got to her feet, exteding a hand up. He took it and nodded. ``And a lift home?''

``I'm staying at the barracks tonight.'' 

``Do -- alright.'' She said and then did not say, because it wasn't like you could argue Link out of Royal Duty. ``Meet me later in the day then. To discuss your problem.'' \emph{Euphemisms} she sputtered in private disbelief. She was using euphemisms. 

``Why not the day after, instead? I'd rather deal with this on full day's rest.'' 

``Deal!'' she said with far more vehemence than she meant to, and kicked off the ground. In the glowing acorn light below, she saw Link waving goodnight, and saw the turtle slip back in the water. 

\vskip 4ex
\lettrine[lines=3]{A}{bove the clouds} the wind blew too sharp and frore to keep her eyes open. Irene pulled the brim of her hat far down and retreated into her cloak, relying on memory to navigate home half-blind. It worked, and in half an hour her boots touched soggy ground and she stood outside her hut, immiserated and shivering. 

An oil lamp burned in the window, which meant Gram was already asleep -- and also that Gram had come around on upgrading from monster tallow, which Irene had not been expecting for months yet given how vehemently she'd insisted the smell was an essential part of a witch hut's ambiance when Irene last raised the subject. Light -- warm, amber, and stenchless -- filtered out across the cottage stoop, and in its glow something glass shone. The lamp might have been brighter than candles, but not bright enough to reveal any more as she approached than what she already had guessed: bottles, six of them, sat neatly arrayed on the first step of the entrance. 

When did he find time to leave them?

Carrying the bottles underarm, she ascended the stairs two at a time before skidding to a stop at the door. She elbowed the latch up, the door swung inward, and in a trice she had the bottles spread out over the work table. Lamplight did plenty up close, and now she could see chuu jelly climbing the glass, meniscus bowed deep, in one, but not a color she'd seen before. She swirled it in the glass --less viscuous than she was used to, as well.  The next bottle was double-sealed with an inscription in what was \emph{probably} Old Labrynnan to keep the poe in. Gram would want to have the first look at that. Then there were peahat leaves, second flush by the smell of them, who knows where he'd found that but she could cure every sore throat in Hyrule for years coming with a batch this plentiful. The bottle after held hairs off a lynel's tail, and she hrrmed quietly because truly she wished he hadn't risked the trouble of getting them. Then there was a clutch of terrorpin eggs, not remotely magical but she'd always wanted to try them in stew. And then--

There was something in the last bottle, but scarcely enough something to see. She could turn the glass under candle light and in the movement catch a rainbow-colored shimmer off of whatever was inside, but holding it still revealed nothing more. Rotating it back and forth the same flash of light ran up and down the center of the bottle no wider than a hair's breadth, which gave her at least a hunch to go on. 

The bestiary was on the other table, but its pages were folio-sized and it weighed like a boulder, and if she ever dropped it Gram would let her have it, so it was easier to carry the lamp and bottle over to it than move the book. She waited a patiently for her hands and sleeves to dry before touching the pages, then waited impatiently, and after five minutes muttered a piece of \emph{drý-cræft}\marginnote{Old Eng. for `sorcery', that it's magic to dry her is just a bad pun and coincidental.} 
under her breath. Gram turned in her sleep, but did not wake. As quietly as she could, Irene leafed page by page until she came to the illustration and accompanying text she was looking for:

\begin{quote}A phantome that represents a hunger lingering vpon the earth. The Pol's uoice stands two feete of height, but with its eares held tall may stretch to four. Being ghostlie, it may eat any food and leave the likeness of the meal still on the earth, but any who eat the same meal after gaine no nourishment. Its whiskers are extreamlie fine of texture, and shine in colours sympathetick to whosoeuer holds them ahand. When they are added to a preparation of Metheglyn, after it has beene set on the fire but before it has come to froth, the drink can cure any maladie; but the whiskers haue power onely if severed from a living animal (if any Pol's uoice may be soe called), which by the creature's great fortitude is alwaies a wearisome and dangerous uenture. The Venerable Beedle (liber. iv, ch. xi) says that oft the Pol's uoice and the Poe spring from one soule, which vpon death becomes diuided into severall partes, the Pol's voice being the parte of a desirous will, the Poe being the parte of an inueterate malice, and further prooves the point by obseruing that `Pol' and `Poe' are descended from the Sheikah \emph{Poi}, and that in many lands the two names doe signifie the same monster.\end{quote}
Irene carefully removed the stopper, plucked out a strand between two fingers, and, holding it in front of the lamp, saw the whisker darken until it matched the black of her cloak. She knew, distantly, this meant she could do worlds of good but the only thought she could actually form and put to words was that this was just like the lynel tails. Worse, even, because you could at least kill a Lynel before collecting the tail. Link was in danger and whatever instinct made people jump to save themselves, he'd lost it. Which meant that if anyone was saving him, it had to be her.

She sat and stared at the whisker in her hand for a small eternity.

What would Gram do? Not be caught in this situation in the first place, because she wouldn't tell fortunes for a lark. Well, what would Gram advise another witch to do? Drop dead, because she had no truck with fortune telling at all. Damn. Then, what would an alternate version of her Gram who didn't hate palmistry say? Irene strained her imagination to no avail, but maybe she didn't need to imagine. She had never travelled that far from home before, but if she set out early enough she might even be back by morning, to say nothing of the other advantages of her rapidly-forming plan. 

Self-respecting witches did not meddle, her Gram had drilled this into Irene at the earliest age possible. Self-respect\-ing witches did not bless infants with good character or with the ability to talk to animals. Self-respecting witches did not guarantee good harvests, nor did they guarantee anything. Self-respecting witches especially did not try to shape people's futures; and if a self-respecting witch's daily reading of chuu jelly \emph{did} happen to mention some idiot thane destined to become king, she kept it to herself.\marginnote{I really like this joke, but it might be too out-of-world.}
Irene intended to break none of these rules, now or ever, but also knew better than to hope that Gram, if she ever learned of it, would see the nuances of the present situation.

She likewise was under no illusions that, when Royal duty next found him and Link next vanished for weeks into the monster-infested wilds and returned, as he always did, stuffed impossibly and insufferably full of gossip, word of her visit would somehow not be among the scores of rumors he gathered like rupees. Nor did she have any question about the sense in which the rumors would run; a young woman asking after the fortune of a man her age was even more certainly doomed to romantic misinterpretation than a princess paying honor to her most favored knight. It had ever been thus, but now, only a year or two away from her apprenticeship's end and setting out as a witch in her own right, it was harder to endure.

In light of the stubborn facts, Irene had taken no time at all to decide that there would be no rumors, nor a stern talk from her Gram about pride in her craft, and if it required traveling a world and a half away, well this was hardly any distance at all to a good broomstick.

It remained a great deal of distance to a young witch.  

%\begin{fragment}
%In Link and Zelda's telling, Lorule was a land precisely unlike Hyrule in a thousand small ways which added up to a deep, untraceable family resemblance. This description was true, but only in the same strict and literal sense that, with enough great-grandparents, she shared a family resemblance with pond moss. Lorule was not some distant cousin of her home, or the reverse to Hyrule's obverse, it was an imposter, and bore no more relation from being different than pigtails did to hogsheads. She marveled that neither Link nor Zelda had noticed this. 

%The Kingdom of Lorule disguised itself poorly and, beyond the copy-cat placed rivers and mountains, was completely dissimilar to the tranquil and prosperous Kingdom she knew. Here was a land pockmarked with hermit-crab towns. A kingdom whose villages' borders stopped dead at the sight of woods and bramble. Whose rivers were left unbridged and footpaths left to overgrowth. Highways that went, even with the canyons gone and curses lifted, without the stamp of a single footprint. Even from the air she felt claustrophobic. Landing, in front of a tiny yellow tent in a grove of trees warped over themselves was worse.
%\end{fragment}
\end{document}

