\documentclass[../../FGP.tex]{subfiles}
\renewcommand\thepage{\arabic{page}}
\begin{document}
\section{Hygge}
Suspicions had been growing in the back of his mind since lunch when the jam in his Chu roll -- made fresh before Irene started divination sessions that morning, and from berries he had picked and preserved no more than two days ago -- tasted weak of flavor. Later in the afternoon, just as the sun reached its zenith and the day grew its hottest, he absentmindedly traced the tips of his teeth with his tongue after a glass of water and thought them unusually sharp. He looked back to the hut and heard the murmurations of a fortune in progress before noting the line stretching out the door. On the principle of better safe than sorry, he had quickly extinguished the fire and dumped back his pile of unused coals into the covered bin, before setting himself to at least hammering out the general shape of an oxshoe with the last hot bits of metal. After that he spent an hour cleaning, and another clearing monsters in the surrounding wood before stopping to rest, and only when the sun was half-down and casting pallid rays of blurry indistinct smudge on the horizon was he certain.

The cottage door was shut tight when Link arrived, which meant Irene was still giving counsel. An elderly Zora rested against the shady side of the house, while a young girl paced out the edges of its umbra.

``Either of you here for an emergency?'' he asked, knowing full well that they were not, but getting them to say that they'd been triaged to the back of the line always made cutting in front easier.

The Zora blinked alert, ``Just a refill on eye-dr--''  

``\emph{Myfriendisdying}'' 

``Where are they?'' Link asked immediately, without quite catching the reassuring evenness of tone Irene would use.  %slipping into triage mode, collecting basic info, and also don't want to out and out say it but this question is at least partially to save Irene a trip if the patient is too far away to help in time.

``Here!'' she nearly screeched, motioning to the ground next to her. Behind her, the Zora  switched to its other pupils and muttered in confusion.

Link wished again that he still held the hint glasses, but by now a sniff of the air was nearly as good and confirmed what his eyes already told him.

``I see, and when did they start feeling sick?'' he said, already reaching for an empty bottle regradless of the answer. 

``In the morning. They said their tummy hurt, and then while we waited it got worse.''%OK SO: Possible Answers
% What're they dying of? Where are they?
%    What're they dying of is Triage question both for info and also "raise 'em from the dead if the croak" folks though I think that has to be subtext

``An acute case of Rapid-Onset Tummyhurtosis'' Link offered in his best diagnostician's voice. ``A rare but serious condition for invisible friends. But easily treated with colorless red poti--''

The empty bottle was snatched out of his hands before he could finish speaking. 
%---

% Irene rambles logistically trying a lot of suggestions all of which involve heavy, taxing magic (Transport herbs and care package by Sending, Transport Link by Sending, make both trips herself,* Try summoning Link back by magic, distant health ritual on Not-Gram, ... )
% * On a broomstick that probably isn't that challenging on its own, but let's say that it becomes quite difficult if another witch has laid claim to the airspace you want to travel in (as Not-Gram has around her hut). 


``Every single one of those sounds \emph{exhausting}.'' Link fought back a laugh of incredulity, but not successfully. 

``At least let me -- here'' her hand glowed bright and blue with the
kind of magic he was trying to get her not to use. ``\emph{Dýrling},'' she said, tapping his chest before he could object. The spell of protection came over him in a warm breeze, and he marvelled again at how easily she switched between phonologies.\marginnote{i.e., switched the sets of sounds -- intonations, accents -- used. maybe just say accent?}
\end{document}
