\documentclass[../FGP.tex]{subfiles}
\renewcommand\thepage{\arabic{page}}
\begin{document}
\setmarginpargeometry
\section{Princess}
\begin{fragment}
Irene woke in darkness and waited for her eyes to adjust. It was unseasonably warm for early spring, especially when the sun had not yet risen, and she wondered at what weather might have rolled in along with the unexpected heat. Wind? Rainstorms? But there was no faint wail of air through the cottage shutters, nor the gravelly hiss of droplets on the roof. Birdsong filtered through the closed windows, which settled the matter -- if there had been storms they were gone now. It also meant that there should at least be the beginnings of a dawn outside, so why could she not see yet?

She pulled herself up straight and the quilt, a scratchy thing as old as the Great Witch Syrup, slid with uncharacteristic fluidity onto her knees still in covers. Extending her arm to her left -- slowly, so as not to hit Gram if she was sitting awake -- Irene outstretched her fingers and tried to move a bit of flame from the hearth's embers into the wick of the candle they kept by the bedside. Warmth neither came in to her nor flowed out. Irene fumbled around in the substratum of all things for the objects she was trying to connect and found nothing. No candle, no hearth. With nothing to do she let her arm flop back down, and when her palm hit the mattress she noticed the third absence. No Gram.

Irene leapt, or tried to. The side of her jaw flashed in pain and the bone of her wrist hit hard against something cold and smooth. She kicked and kicked uselessly against the air and her foot, still tangled in blankets, moved half an inch at most. Her other hand, the one that wasn't stinging, had also somehow smothered itself in blankets and it flopped like a fish as she tried to reach for something, anything in the dark to help her get her bearings back. It brushed something alternatingly soft and solid in a corded texture. She grabbed it by reflex. What on earth was \emph{that}, why did this quilt go on \emph{forever} and where was Gram and \emph{why couldn't she see?} 

% So this actually may be a lighter rework than it seemed last night.
% - Falls out of bed in a panic, (Check!)
% - Blinded (Revise)
% - Sees a tiny bit of the room. Only that it is _vast_ and there is a figure entering from the far side of the room
% - quilt back over eyes
% - 'Highness?' resumes
The curtains around her bed opened with a terrible rattle and Irene traded blinding dark for blinding sun. A palatial room and a distant figure, entering from the far side of it, burned against her eyes before she slammed them shut and pulled the quilt back over her face. 

``Highness?" A voice -- the figure's -- asked with poorly masked confusion.\marginnote{Come back to the section and try to distinguish the voices by sound more than repeated 'first' and 'second'}

\reversemarginpar``Wise one?"\marginnote{I'm also considering: Vitrsta \emph{Wite}? and \emph{Witestre}? (female cognates of Old English \emph{Wita}, wise man, advisor) and \emph{Wicce}? (Old English for witch).} Another voice, stationed somewhere off to Irene's left, asked with no mask at all.

\emph{I'm not a}-- but plainly she somehow was, so Irene swallowed her panic and gathered up her most cooly regal voice. ``We are awake,'' she announced, raising her voice to be heard over the quilt's muffling. The voice out of sight burst into peals of laughter. Irene felt her lips tighten into a scowl. She had enough problems without being the object of someone's fun.\marginnote{TOO BLUNT}

``And uninjured?'' The first voice again.

``And uninjured'' she snapped. Irene pulled the quilt down yet again, slow enough to allow her to prepare for the sun this time, and glared where she expected to see them. ``Glad it's a laughing matter to you both, though.''

She immediately regretted it. The face of a girl maybe four years her junior 
    % Sees Lyria, who is maybe three years younger than her looking stricken. 
    % Not sure if she snaps back in reply, I think probably yes, but then gets a handle on it and reins in anger
    % Reminds self things are perfectly normal to them.
    % Apologises. Which is a wrong move in a different direction because royalty doesn't admit error.
    % Witch asks if they can brew witestre something. A short morning soup perhaps.
    % Irene replies she wishes to consult her Grandmother
    % Silence.

    % -Lyria: HRH Hylia Themiskopa Hyrule, mother of Zelda Hyrule III, grandmother and namesake of princess Eirene Themiskopā Hyrule, has been dead ten years.
    % -Lorain: Your other gram's kicked it, too. ...sorry.
    %   OK COOL IDEA HERE: WITCHES TALK VERY CONVERSATIONALLY _SPECIFICALLY_ WHEN ON THE JOB. ALSO OFF THE JOB, BUT LIKE, EXTRA SO ON THE JOB.

% Looks around the room. It is a massive solarium. 
% Not sure which order she sees these in
%    - Stained glass dome. Analemmatic dragons on top. Divided into seven
%    - Walls closer down alternate with great windows looking out onto all of Hyrule below. Room is a heptagon and each side is equal parts window and wall. Dividers of dome meet at vertices of the heptagon.
%     - No really just massive. Has subcomponents: Hearth with large fire, mini-library and desk, observatory, public balconada, servants area,  

% - Her bedroom was a small, book-drowned thing with wooden floors. It was debatable whether she had a bedroom at all, since if she did it was also a kitchen, study, receiving room, and Gram's bedroom as well. This was nothing of the kind. 

% Another witch, tending the cauldron -- her cauldron -- by the hearth, which is not where it should be.
%she looked back up at a rose window set into the ceiling.
% - Divided into seven, one for each color of the rainbow, natural phenomenon motifs in each
%    Don't think it'll come up but:
%      - Red (Fire)
%      - Orange (Ferromagnetism)
%      - Yellow (Light)
%      - Green (Plant growth)
%      - Blue (Ice)
%      - Indigo (Water)
%      - Violet (Gravity)
% -Five Dragons curling through the panels in double-loops. They're analemmata, but where's she supposed to view from? And how to tell which dragon meant which time? Link would know. He'd probably also be able to interpret the symbols on the tracery of the window. He's still in Labrynna for two days, but maybe if she ambushed him on his return before he could be sent off again. 




 %It's a bedroom, Jim, but not as we know it

%- sun is coming down through an elabroate stained glass window
%- ...which has an analemma on it. And other markings. Link would be able to identify what time it was, which was moot because he was in the barracks. Maybe she could make a sketch to bring to--
%- ...where is she???


\end{fragment}
\begin{fragment}
On her third day, Irene came to the conclusion that Being Witch-Crown Princess was an endless exercise in costuming. She was still unsure whether she held one title or two, but she was beginning to believe it must be two because her attendants only ever helped her dress for the princess half, and then left her to find an appropriate cloak and hat by herself. But then what witch owned so many different styles of cloaks and hats, and how ever was she supposed to fit her crown over the point of her hat without assistance? Lorain visited in the mornings and offered breakfast -- always stews or porridges, always from the cauldron that 
\end{fragment}
\end{document}
