\section{Link}
  \subsection{Problems/Motivations}
  This poor guy is tired as hell and still has obligations. I am going to be spending a lot of time playing up his cattiness, but one respect that he is distinctly un-feline is his generosity and willingness, at any moment, to do work. When H.L. Mencken observed that ``[he] was born, happily, with no more public spirit than a cat,''\footnote{\textsc{H.L.~Mencken, Newspaper Days: 1899--1906}, at v, vii (1941).} I can think of no statement less apposite to Link. A good deal of this story is this poor nut learning to set some boundaries. 
  \subsection{Character Questions}
  \begin{enumerate}
    \item\textit{What’s the lie your character says most often?}
        Probably not in exactly this many words, but ``I'm not over-worked.''  Gulley, the Blacksmith family and most definitely Irene all notice and point out to him that it seems like Royal duty is taking up a concerning amount of his time, but he says he's fine. Really he's fine. He's not always exahausted. He's just doing his duty. He desperately doesn't need a vacation.
    \item\textit{How loosely or strictly do they use the word ‘friend’?}
        Link falls on the stricter side, and though he has warm relations with lots of people, I think he only counts you as a friend if he spends subtantial time with you. Given the way his destiny cuts severely into leisure time, I think this means most of his friends are either in the Royal Guard or are people with whom he has worked overseas (friends in Labrynna, Friends in Hytopia, etc.). Within Hyrule, I think he counts Gulley and Irene as friends outside of his new work.
    \item\textit{How often do they show their genuine emotions to others versus just the audience knowing?}\label{link:characterq:masking}
        Link will often put on a brave face, but won't conceal the direction of his emotion. So fear may come out as mild concern, but it won't be completley hidden. 
    \item\textit{What’s a hobby they used to have that they miss?}
        Back in the days when he had free time Link was a reader, and owned a few older volumes of poetry and prose in the \emph{Chrestomathy};\footnote{I don't remember if I've fleshed this idea out in the World section above, but the Chrestomathy is a long compilation of the development of the Hylian language, often using different versions of the story of the Hero to document changes in the language. The Book of Mudora is one of several tales in the series.} he also misses being a blacksmith -- not necessarily the working hours, but having a manual craft that keeps his hands busy and produces something he can see he's done at the end of the day.
    \item\textit{Can they cry on command? If so, what do they think about to make it happen?}
        He can! He thinks back to the view from atop Death Mountain in Lorule, looking out over everything in the world falling apart and the wind howling. He's seen plenty that's scary, but nothing has every felt as forlorn as that. (He could also think about how he lost his parents,\footnote{\textit{See} \ref{link:characterq:etiquette}, \textit{infra} at \pageref{link:characterq:etiquette}.} but he frankly tries not to think about that at all ever).
    \item\textit{What’s their favorite [insert anything] that they’ve never recommended to anyone before?}
        The stream of colors as he crosses worlds is actually very pretty when you have the time to stop and appreciate it, but the aura from the portal into Misery Mire is the best. He's never really suggested anyone go to Lorule via the scenic route, though. 
    \item\textit{What would you (mun) yell in the middle of a crowd to find them? What would their best friend and/or romantic partner yell?}
        For strangers -- you might fake calls for help I suppose. Irene is direct enough to probably shout ``Hey Link!'' or ``Greenie!'' but that may also be my lack of imagination talking since I struggle with the premise of this question.\footnote{See griping in Irene's Question \ref{irene:characterq:yell}, \textit{supra} at \pageref{irene:characterq:yell}}
    \item\textit{How loose is their use of the phrase ‘I love you’?}
        Paradoxically, I think this is looser for him than who he counts as his friends: he's completely ready to tell any of his friends that they're loved, and in addition he has at least four different mentor and parent figures he doesn't think of as friends who he would say he loves as well (Blacksmith and his Wife, the Witch, and Sahasrala). 
    \item\textit{Do they give tough love or gentle love most often? Which do they prefer to receive?}
        Mostly being raised by the Blacksmith and his family, Link is very used to tough love, but I think wouldn't mind receiving some of the softer stuff. He is always happier giving small gifts or doing small favors, and in his own expression definitely finds soft love as the more natural avenue. 
    \item\textit{What fact do they excitedly tell everyone about at every opportunity?}
        Irene is the greatest witch of her generation. This is old news within Hyrule,\footnote{It is partly old news because he has told so many people} and when he is closer to home he's eager to talk about specific new potions and enchantments Irene has come up with, but when he's out on diplomatic work he has to start with the basics: he knows an amazing witch who is unbelievably talented. I think there's very little Link gets to enjoy about most of his travels after he becomes so famous: He likes parts of adventuring out in the wilderness, but most of his assignments after the game are to meet and help some dignitary in a town, so the biggest positive of his job is getting to talk up his friend wherever he goes.
    \item\textit{If someone was impersonating them, what would friends / family ask or do to tell the difference?}
        There is a simple, fool-proof way to find the real Link. In the morning, leave Link and the imposter to their own devices. Whoever wakes first is the faker.
    \item\textit{What’s something that makes them laugh every single time? Be specific!}
        From up close, lynels are terrifying. The least favorite of his enemies. 
    \item\textit{When do they fake a smile? How often?}
        When representing the crown and glad-handing misc.~dignitaries, all the time. Because of that, however, I think he is conscientious that in his limited ``off'' time he doesn't fake an insincere emotion.\footnote{Though he does, sometimes, regulate or mask the intesity of what he feels, see question \ref{link:characterq:masking}, \textit{supra} at \pageref{link:characterq:masking}.}
    \item\textit{How do they put out a candle?}
        He leans over, takes a deep breath in, and extinguishes it with one big puff. 
    \item\textit{What’s the most obvious difference between their behavior at home, at work, at school, with friends, and when they’re alone?}
        When by himself or with Irene, he becomes demonstrably more of a gremlin: grazing out of pantry foods without fixing a proper bowl, sitting on whatever comfortable object will hold him as opposed to proper chairs, sneaking from the more edible potion ingredients. Notably this is purely driven by who is in his company: Gram can enter the room and he will immediately assume good manners and be such a nice young boy, and then she'll step out and he will go back to grazing. Irene, a covert gremlin herself, finds it hilarious.
    \item\textit{What kinds of people do they have arguments with in their head?}
    \item\textit{What do they notice first in the mirror versus what most people first notice looking at them?} 
    \item\textit{Who do they love truly, 100\% unconditionally (if anyone)?}
        Irene. Probably also Gulley and the blacksmiths who are a lot like adoptive family, but it's made just a tiny bit weird by them also being former employers.\marginnote{Maybe Gulley and not the blacksmiths? I keep going back and forth on this.} After this story is over I think he and Zelda become incredibly close friends and she appears on this list later. And likewise I think if he had more time to see Gram/The Witch she'd be on this list, but until after the story is over the amount of travel he does means he just doesn't see her often enough for her to be adoptive family too.
    \item\textit{What would they do if stuck in a room with the person they’ve been avoiding?}
    \item\textit{Who do they like as a person but hate their work? Vice versa, whose work do they like but don’t like the person?}
        Both milk bar owners are perfectly tolerable people, Link thinks, but neither has a product he can stand. He stops by to say hello some times, but rarely actually buys a glass.
    \item\textit{What common etiquette do they disagree with? Do they still follow it?}\label{link:characterq:etiquette}
        Before the plague, when he had parents, Link would set muddy boots just inside the door. He'd get scolded, and then he'd do it again because a muddy inside was better than damp boots that spent a night outside on his feet. Hyrule runs on a miasma theory of epidemiology, and though he tries not to dwell on it he's consumed with guilt that he might have tracked the illness indoors to this day and though he hates it, always leaves his boots out when they're dirty now.
    \item\textit{What simple activity that most people do / can do scares your character?}
    \item\textit{What do they feel guilty for that the other person(s) doesn’t / don’t even remember?}
    \item\textit{Did they take a cookie from the cookie jar? What kind of cookie was it?}
        This kid will smash the cookie jar open like a clay pot just to see what might be in it. I think he is hoping for oatmeal raisin, but he is not picky.
    \item\textit{What subject / topic do they know a lot about that’s completely useless to the direct plot?}
    \item\textit{How would they respond to being fired by a good boss?}
    \item\textit{What’s the worst gift they ever received? How did they respond?}
        Link is trapped in a recurring nightmare. Wherever he travels foreign dignitaries want to honor him, so they give him a sword. \emph{Another} sword. Link has one very well-maintained sword that he uses, and he doesn't particularly like using it. He very diplomatically thanks whatever potentate, accepts the sword, carries it home, and prompty gives it to the blacksmith for scrap. He spends the rest of his life worrying that someday the potentate will visit Hyrule and notice their sword isn't displayed in some place of honor.
    \item\textit{What do they tell people they want? What do they actually want?}
    \item\textit{How do they respond when someone doesn’t believe them?}
    \item\textit{When they make a mistake and feel bad, does the guilt differ when it’s personal versus when it’s professional?}
    \item\textit{When do they feel the most guilt? How do they respond to it?}
    \item\textit{If they committed one petty crime / misdemeanor, what would it be? Why?}
        Link will never stop breaking and entering.
    \item\textit{How do they greet someone they dislike / hate?}
    \item\textit{How do they greet someone they like / love?}
    \item\textit{What is the smallest, morally questionable choice they’ve made?}
    \item\textit{Who do they keep in their life for professional gain? Is it for malicious intent?}
    \item\textit{What’s a secret they haven’t told serious romantic partners and don’t plan to tell?} 
    \item\textit{What hobby are they good at in private, but bad at in front of others? Why?}
    \item\textit{Would they rather be invited to an event to feel included or be excluded from an event if they were not genuinely wanted there?}
        Excluded. Give him his free time back if he doesn't want to be there, please.
    \item\textit{How do they respond to a loose handshake? What goes through their head?}
    \item\textit{What phrases, pronunciations, or mannerisms did they pick up from someone / somewhere else?}
        The names of lots of animals in Eastern Hyrule he learned from Irene, and since she tends to shorten the vowels in those names, so does he. 
    \item\textit{If invited to a TED Talk, what topic would they present on? What would the title of their presentation be?}
    \item\textit{What do they commonly misinterpret because of their own upbringing / environment / biases? How do they respond when realizing the misunderstanding?}
    \item\textit{What language would be easiest for them to learn? Why?}
    \item\textit{What’s something unimportant / frivolous that they hate passionately?} 
    \item\textit{Are they a listener or a talker? If they’re a listener, what makes them talk? If they’re a talker, what makes them listen?}
    \item\textit{Who have they forgotten about that remembers them very well?}
    \item\textit{Who would they say ‘yes’ to if invited to do something they abhorred / strongly didn’t want to do?} If there is a colorable argument that the request is part of his duty as a hero, he'll do it no matter who asks. If there isn't an argument that this is part of his duty, he tends to set his feet in pretty well because he already does so much he doesn't want to on the job.
    \item\textit{Would they eat something they find gross to be polite?}
        For sure.
    \item\textit{What belief / moral / personality trait do they stand by that you (mun) personally don’t agree with?}
    \item\textit{What’s a phrase they say a lot?}
    \item\textit{Do they act on their immediate emotions, or do they wait for the facts before acting?}
    \item\textit{Who would / do they believe without question?}
        Irene. I think he also would believe that the Blacksmith and Gram would never deliberately lie to him, so in some sense what they were saying must be true, but he thinks both of them are much more likely to be honestly wrong or say something inaccurate than Irene.
    \item\textit{What’s their instinct in a fight / flight / freeze / fawn situation?} 
    \item\textit{What’s something they’re expected to enjoy based on their hobbies / profession that they actually dislike / hate?}
    \item\textit{If they’re scared, who do they want comfort from? Does this answer change depending on the type of fear?}
        The hero complex is making this poor guy's life so much harder than it needs to be. Because he spends so much time saving the day, he tends to associate fear with imminent danger, and though he can handle imminent danger, he doesn't want other people put in peril, so when he feels scared or anxious he tends to self-isolate out of habit. 
    \item\textit{What’s a simple daily activity / motion that they mess up often?}
    \item\textit{How many hobbies have they attempted to have over their lifetime? Is there a common theme?}
  \end{enumerate}