\section{Zelda}
  \subsection{Problems/Motivations}
  Before I go and drop her in the wilderness uprepared, I don't think Zelda is aware she has problems as such. She would certainly concede to dissatisfactions: a too-small peer group, a far-too-stressful workload, a lack of variety in her life, but she's princess of Hyrule and with all that's given to her, who is she to complain or count them problems when so many people -- quite arguably, literally \emph{all} people -- have it harder than she does?  But call her pains what you like, Royal life is burdensome, monotonous, and isolating. Another force preventing her from frankly naming her problems is that it is hard to do so without sounding like she resents being given a unique ability to do good for all of Hyrule, which is something she sincerely wants -- at least in theory. The divergence between theory and practice is this: she isn't doing much good as Princess, and at some subconcious level she knows it. All these problems share a common root: an impulse to over-mythologize the chain of Zeldas has warped the priorities of ruling into a regime that is both too confining and too personalist. 

%  understanding of being a Princess merely from a position of power to one of of put frankly insane expectations on her, and at the same time completely mistrained her for administering a country in the sense that the greatest emphasis in that training is adjudicating disputes with her wisdom, and while she's empathetic and does this adequately, I don't actually think she has the life experience to be good at it, or to really productively use her role as Queen of Hyrule to improve the country writ large (there are numerous stumbling blocks here, the first of which is she doesn't see the need to do those improvments and the next of which is it'd mean hiring a lot of staff and she feels a lot of pressure against this because she's wise and runs the whole country by herself and isn't that what the Goddesses wanted?)
  \subsubsection{Isolated}
%  \subsubsection[Hello in There]{Hello in There\footnote{\textit{Cf.} \textsc{John Prine}, \textit{Hello in There}, \textit{on} \textsc{John Prine} (Atl.~Records, 1971), which is not the vibe I thought Zelda's character would start with, but here we are, one more part of this story going off out of control.}}

  \subsubsection{Ineffectual}
  \subsubsection{Attitude toward Destiny}The Goddesses have a plan, which is unfolding even now and this is a source of enduring comfort to Zelda. The Goddesses will, at times of need, provide means to address whatever problem -- large or small -- arises. On this read, it is important to be alert for divine gifts the Goddesses might send, and to carry out one's duties sedulously, but there isn't an implied striving or pressure to go out into the world and find what you should be doing. Another way to frame this is to say that Zelda generally thinks the Goddesses have put people where they ought to be, and where they are most able to do good by being themselves, and the world will for the most part naturally hum along in harmony, with her needing to intervene on occasionally. This all is decidedly Panglossian, but it fits well with a lot of the Royal Family's self-mythologizing which she's been reading all her life.
  \subsection{Character Relations}
  \subsubsection{Link}
  \begin{quote}Castle Guard
  Did you see the paintings here in the hall? They tell you of Hyrule’s oldest legend.

  But all that happened so long ago. Sometimes I wish I could go back to the past to see if it’s true!\end{quote}

  \begin{quote}
  Castle Guard
  The princess runs the whole country all by herself. Can you imagine, and at her age too?

  When I was that young, I spent my days doing nothing but chasing Cuccos. 
  \end{quote}

  \begin{quote}Rumor guy
  Everyone, not just the rumor guy but attendants and servants too, seems to read romantic intrigues into Zelda's nighttime wanderings. When someone follows Zelda one night, they find "[the princess] stopped in front of a large painting on display in the center of the castle. And she stood there just staring up at the painting for 10 minutes. And then went back to her room."  
  The painting, we're told, depicts "a hero and princess from several generations ago cuddling in one another’s arms\ldots" and "The painting brought out a look of such admiration that had never been seen before in the princess." We do not have to accept either characterization at face value. It seems likely, though not certain, the large painting is painting V of the sequence we see at the start of the game. It shows a Zelda, gazing up in wonderment at a Link and it could easily be given romantic overtones but it does not show them cuddled up. There might be another painting elsewhere in the castle, but it seems equally possible that this is a case of the image being refracted in popular vision, like Mennochio and the Fioretto della bibbia.\end{quote}


  You know what? Scratch that skeptical note. Yeah. She \emph{is} projecting a lot of fantasies on to this poor green guy! Honestly fair. If I was running a country all by myself at 12 or 13 I'd want company too, and I'd be a little crazy by 15 or 16 as well. She lives alone in a castle and has an attendant to talk to and no one her age!
  And then all her life there's lots of Destiny talk that she's going to be really close with this green guy? Sign her up!
  \ldots only they don't seem to be?
  He's nice, she's nice, they talk idly, but it's transactional.
  And empty transactional. Pleasure doing business with you.
  The rumor monger in LBW hints pretty well that There's a level of romance and yearning on this one and I'm not saying otherwise, but man I think I'd have a yearning that runs the full gamut if I were that locked up, and I think there's a level of that ``want to be/want to date'' confusion with Link who is so adept at charming people along his travels and so naturally social. Anyway, I think there's a relation here but it is oddly parasocial and projective, and that's not really her fault, but it does me she needs to get out more.
  \subsection{Character Questions}
  \begin{enumerate}
    \item\textit{What’s the lie your character says most often?}
    \item\textit{How loosely or strictly do they use the word ‘friend’?}
    \item\textit{How often do they show their genuine emotions to others versus just the audience knowing?}
    \item\textit{What’s a hobby they used to have that they miss?}
    \item\textit{Can they cry on command? If so, what do they think about to make it happen?}
    \item\textit{What’s their favorite [insert anything] that they’ve never recommended to anyone before?}
    \item\textit{What would you (mun) yell in the middle of a crowd to find them? What would their best friend and/or romantic partner yell?}
    \item\textit{How loose is their use of the phrase ‘I love you’?}
    \item\textit{Do they give tough love or gentle love most often? Which do they prefer to receive?}
    \item\textit{What fact do they excitedly tell everyone about at every opportunity?}
    \item\textit{If someone was impersonating them, what would friends / family ask or do to tell the difference?}
    \item\textit{What’s something that makes them laugh every single time? Be specific!}
    \item\textit{When do they fake a smile? How often?}
    \item\textit{How do they put out a candle?}
    \item\textit{What’s the most obvious difference between their behavior at home, at work, at school, with friends, and when they’re alone?}
    \item\textit{What kinds of people do they have arguments with in their head?}
    \item\textit{What do they notice first in the mirror versus what most people first notice looking at them?}
    \item\textit{Who do they love truly, 100\% unconditionally (if anyone)?}
    \item\textit{What would they do if stuck in a room with the person they’ve been avoiding?}
    \item\textit{Who do they like as a person but hate their work? Vice versa, whose work do they like but don’t like the person?}
    \item\textit{What common etiquette do they disagree with? Do they still follow it?}
    \item\textit{What simple activity that most people do / can do scares your character?}
    \item\textit{What do they feel guilty for that the other person(s) doesn’t / don’t even remember?}
    \item\textit{Did they take a cookie from the cookie jar? What kind of cookie was it?}
    \item\textit{What subject / topic do they know a lot about that’s completely useless to the direct plot?}
    \item\textit{How would they respond to being fired by a good boss?}
    \item\textit{What’s the worst gift they ever received? How did they respond?}
    \item\textit{What do they tell people they want? What do they actually want?}
    \item\textit{How do they respond when someone doesn’t believe them?}
    \item\textit{When they make a mistake and feel bad, does the guilt differ when it’s personal versus when it’s professional?}
    \item\textit{When do they feel the most guilt? How do they respond to it?}
    \item\textit{If they committed one petty crime / misdemeanor, what would it be? Why?}
    \item\textit{How do they greet someone they dislike / hate?}
    \item\textit{How do they greet someone they like / love?}
    \item\textit{What is the smallest, morally questionable choice they’ve made?}
    \item\textit{Who do they keep in their life for professional gain? Is it for malicious intent?}
    \item\textit{What’s a secret they haven’t told serious romantic partners and don’t plan to tell?}
    \item\textit{What hobby are they good at in private, but bad at in front of others? Why?}
    \item\textit{Would they rather be invited to an event to feel included or be excluded from an event if they were not genuinely wanted there?}
    \item\textit{How do they respond to a loose handshake? What goes through their head?}
    \item\textit{What phrases, pronunciations, or mannerisms did they pick up from someone / somewhere else?}
    \item\textit{If invited to a TED Talk, what topic would they present on? What would the title of their presentation be?}
    \item\textit{What do they commonly misinterpret because of their own upbringing / environment / biases? How do they respond when realizing the misunderstanding?}
    \item\textit{What language would be easiest for them to learn? Why?}
    \item\textit{What’s something unimportant / frivolous that they hate passionately?}
    \item\textit{Are they a listener or a talker? If they’re a listener, what makes them talk? If they’re a talker, what makes them listen?}
    \item\textit{Who have they forgotten about that remembers them very well?}
    \item\textit{Who would they say ‘yes’ to if invited to do something they abhorred / strongly didn’t want to do?}
    \item\textit{Would they eat something they find gross to be polite?}
    \item\textit{What belief / moral / personality trait do they stand by that you (mun) personally don’t agree with?}
    \item\textit{What’s a phrase they say a lot?}
    \item\textit{Do they act on their immediate emotions, or do they wait for the facts before acting?}
    \item\textit{Who would / do they believe without question?}
    \item\textit{What’s their instinct in a fight / flight / freeze / fawn situation?}
    \item\textit{What’s something they’re expected to enjoy based on their hobbies / profession that they actually dislike / hate?}
    \item\textit{If they’re scared, who do they want comfort from? Does this answer change depending on the type of fear?}
    \item\textit{What’s a simple daily activity / motion that they mess up often?}
    \item\textit{How many hobbies have they attempted to have over their lifetime? Is there a common theme?}
  \end{enumerate}